### 2013-12-22 image_analysis_paper/plos_draft.tex
Added more disucssion to paper

\subsection*{Diffusion Maps}
Unlike PCA, diffusion maps (DMAPS) is a nonlinear dimensionality reduction technique. 
%
DMAPS

\subsection*{Angular Synchronization in $SO(2)$}

>>>>

\subsection*{Diffusion Maps}
Unlike PCA, diffusion maps (DMAPS) is a nonlinear dimensionality reduction technique. 
%
DMAPS aims to uncover the parameterization of data sampled from a nonlinear manifold.
%
The {\em essential} requirement for DMAPS is an appropriate distance metric $d(x_i, x_j)$ for comparing data points. 
%
This can be the standard Euclidean distance, or a more complex metric for other data sets.

We then calculate the matrix $W \in \mathbb{R}^{n \times n}$, where 
\begin{equation}
W_{ij} = \exp \left( -\frac{d^2(x_i, x)j)}{\epsilon} \right)
\end{equation}
and $\epsilon$ is a characteristic distance between data points.
%
In practice, we choose $\epsilon$ to be the median of the pairwise distances between data points.
%
We then compute the diagonal matrix $D$, where $D_{ii} = \sum_{j=1}^{n} W_{ij}$, and the matrix $A = D^{-1} W$. 
%
We then compute the eigenvectors $\phi_1, \phi_2, \dots, \phi_n$ and

\subsection*{Angular Synchronization}

\subsection*{Vector Diffusion Maps}
